---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignteachr

<!-- badges: start -->
<!-- badges: end -->

The goal of `assignteachr` is to calculate and visualize instructor 
workload for the purposes of creating yearly teaching instructor assignments.
This package was built with the goal of doing this for the UBC MDS program.

## Installation

You can install the development version of assignteachr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/assignteachr")
```

## Example usage

Load the `assignteachr` package, 
and any other packages you need (e.g., `tidyverse`):

```{r}
library(assignteachr)
library(tidyverse)
```

Load your course data:

```{r, eval=FALSE}
mds_courses <- read_csv("data/mds_courses.csv")
mds_courses
```

```{r, echo=FALSE}
source("tests/testthat/helper-workload-data.R")
mds_courses <- example_courses
mds_courses
```

Load your section data:

```{r, eval=FALSE}
mds_sections <- read_csv("data/mds_sections.csv")
mds_sections
```

```{r, echo=FALSE}
mds_sections <- example_sections
mds_sections
```

Load your instructor data:

```{r, eval=FALSE}
mds_instructors <- read_csv("data/mds_instructors.csv")
mds_instructors
```

```{r, echo=FALSE}
mds_instructors <- example_instructors
mds_instructors
```

Calculate the workload for each instructor:

```{r}
mds_workload <- calculate_workload(mds_courses,
                                   mds_sections,
                                   mds_instructors)
mds_workload
```

View the workload for each instructor as a bar chart, 
as well as their expected workload:

```{r, fig.height=3}
view_workload(mds_workload)
```

View the balance of each instructor's teaching credits across semesters:

```{r}
view_teaching_balance(mds_workload)
```

